\begin{multicols}{2} 

    \CvSection{Work Experiences}{
        \CvSectionEntry{Lead R\&D Software Engineer}{
            \textbf{Date:} 01/2018 - Present \\
            \textbf{Company - Place:} Cantek Group - Antalya \\
            \textbf{Goal}: Development of Industrial Control Systems (ICS) and Early Warning Systems (EWS) with local
            device or cloud server based web applications for industrial storage and vertical plant factories. \\
            \textbf{Job Description:} \\
            ICS systems are generally managed autonomously by controller devices consisting of PLC or
             electronic cards developed with embedded software. By communicating with the controller devices, 
             the necessary data is sent to the monitoring system designed with micro service architecture in 
             cloud servers. Designing software that offers analytical solutions over large data sets created 
             in the cloud environment, developing it with software and embedded software teams. \\
            \textbf{-} Using Hybrid Database Architectures with combining
            PostgreSQL + Cassandra technologies \\
            \textbf{-} Design and develop Java Microservices with Spring Boot and deploying them as Docker 
            containers on the server \\
            \textbf{-} Configure a system running on the some of Linux distributions
            and apply DevOps using CI/CD Softwares running inside separate Docker containers. \\
            \textbf{|} Managing source code via GitLab \\
            \textbf{|} Compiling Spring Boot applications with Maven via Jenkins \\
            \textbf{|} Serving JARs on the JFrog Artifactory via Jenkins  \\
        }
        \CvSectionEntry{Sn. R\&D Software Engineer}{
            \textbf{Date:} 07/2015 - 01/2018 (2 years 7 months) \\
            \textbf{Company:} Cantek Soğutma - \textbf{Place:} Antalya \\
            \textbf{Goal:} Design and develop local monitoring device. \\
            \textbf{Job Description:} \\
            Fully completed the Local Monitoring System project, which communicates with electronic 
            controllers developed with embedded software, stores this data in its own database and 
            provides monitoring service on the local network. \\
            Technologies I used while developing this project; \\
            Multi-Threaded Java servisleri(Linux deamons) \\
            JSF2.1+Primefaces6+Js+HTML5-Canvas pages \\
            PostgreSql \\
            \textbf{Outcome:} Local monitoring system device was developed and put into service. 
            It was later sold to many countries. \\
        }
        \CvSectionEntry{Computer Engineer}{
            \textbf{Date:} 10/2013 - 11/2014 (1 year 2 months) \\
            \textbf{Company:} Mavi Güvenlik - \textbf{Place:} İzmir \\
            \textbf{Goal:} Managing digitalization processes and implementing software projects. \\
            \textbf{Job Description:} \\
            Studies were carried out through the service and maintenance tenders opened by state 
            institutions such as the Ministry of Justice and PTT. In this context, high security CCTV, 
            handheld biometry and eye biometry devices, tourniquet and x-ray systems were installed 
            and software supported. \\
            In line with the internal and external needs of institutions, we started and successfully 
            completed 2 software projects. \\
            1) Project tracking application to be used in line with company needs \\
            JSF+MySql \\
            2) Desktop application for prison meal organization \\
            Swing + MySql \\
        }
        \CvSectionEntry{Software Developer}{
            \textbf{Date:} 03/2013 - 06/2013 (4 months) \\
            \textbf{Company:} Tez Tour - \textbf{Place:} Antalya \\
            \textbf{Goal:} Development of web applications for agencies and end users. \\
            \textbf{Job Description:} \\
            I have been involved in bug-fixing and developing new modules in web applications actively \\
            serving in one of the world leader companies in the tourism sector. \\
            Spring MVC, JS + JQuery
            \textbf{Outcome:} Digital Transformation of Business Processes \\
        }
        \CvSectionEntry{Jr. Computer Engineer}{
            \textbf{Date:} 2007 - 2010 (3 years) \\
            \textbf{Company:} Mikro Yazılım (KKTC) - \textbf{Place:} Lefkoşa \\
            \textbf{Goal:} Studies on software support staff and information systems. \\
            \textbf{Job Description:} \\
            Micro software installation and technical support task in 'Cyprus Mikro Destek' firm which \\
            is the representative of the Turkish Republic of Northern Cyprus of the micro software house \\
            at the same time, I worked as the assistant of Northern Cyprus Belça Shopping Malls Information \\
            Systems Specialist. \\
        }
    }
    
    \colbreak
    \CvSection{Start-up Projects}{
        \CvSectionEntry{Yazılım VIP (http://www.yazilim.vip)}{
            \textbf{Date:} 07/2018 - Present \\
            \textbf{Position:} Co-Founder \\
            To keep this platform open to everyone who is competent and willing to share what we call an open source world. \\
            A platform aimed at presenting our competencies to the open source world without waiting for a response. \\
        }
        \CvSectionEntry{Goldigo (http://www.goldigo.net)}{
            \textbf{Date:} 03/2014 - 01/2016 (1 year 10 months) \\
            Goldigo was founded in 2014 as an online gaming platform. 
            It was developed as a web application on JSF and MySql as an infrastructure. 
            This platform has been actively used by users from all over the world. 
            It was chosen as the second most preferred platform by Wow players for a period.
        }
    }
 
    \CvSection{Attended Organizations}{
        \textbf{Clean Code Seminar : } Master Seminar \\
        \textbf{ICAIME 2019 : } Participant \\
        \textbf{GDG 2019 : } Participant
    }    

\end{multicols}